Data cleaning for mass mobiliziation data version

### 2024-01-19 Scripts/authoritarian_only.Rmd
intro updates

What I'm looking for here is weak government -> high fraud + narrow vote share -> protest. Not sure if that pattern reveals itself.
```{r}
ggplot(nelda2.sub %>% filter(presidential == 1), aes(x = winner.share.upd, y = v2elirreg.inv)) + geom_point(aes(size=n.events.post)) + geom_vline(xintercept = .5, linetype = 2) + geom_hline(yintercept = 0)
```

>>>>

What I'm looking for here is weak government -> high fraud + narrow vote share -> protest. Not sure if that pattern reveals itself.
```{r}
ggplot(nelda2.sub %>% filter(presidential == 1), aes(x = winner.share.upd, y = v2elirreg.inv)) + geom_point(aes(size=n.events.post)) + geom_vline(xintercept = .5, linetype = 2) + geom_hline(yintercept = 0)
```
Duration as zero-inflated count model (i.e. count of days that protest movement lasted)
```{r}
model.d.base <- glmmTMB::glmmTMB(d.events.num ~ jucon.1lag + legcon.1lag + osorg.1lag + altinf.1lag + libdem.1lag  + natlpartyorg.lag + v2elirreg.inv +  +   v2elirreg.inv + winner.share.upd + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.pre + unscheduled_election + regional_success_lag ,
                                ziformula=~.,
                                data = nelda2.sub %>% filter(inc.lose == "0"),
                                family=truncated_nbinom2)
summary(model.d.base)

model.d.base2 <- glmmTMB::glmmTMB(d.events.num ~ jucon.1lag + legcon.1lag + osorg.1lag + altinf.1lag + libdem.1lag  + natlpartyorg.lag + v2elirreg.inv + gdpgro.1lag  +   winner.share.upd*v2elirreg.inv  + presidential + inc.termlimit.num  +  physinteg.1lag + physintlag.sq + urban.pct + rentierstate + taxstate + n.events.pre + unscheduled_election + regional_success_lag ,
                                ziformula=~.,
                                data = nelda2.sub %>% filter(inc.lose == "0"),
                                family=truncated_nbinom2)
summary(model.d.base2)

sjPlot::plot_model(model.d.base2, type = "pred", terms = c("winner.share.upd", "v2elirreg.inv [-1, 1.5]"))

mydf <- ggpredict(model.d.base2, type = "re.zi", terms = c("winner.share.upd [.2, .3, .4, .5, .6, .7, .8, .9]", "v2elirreg.inv [-.25, 1.5]"))
ggplot(mydf, aes(x, predicted, color = group)) +
  geom_line() 
```
